% Jeffjar's CV
% $ latexmk cv.tex -pdf -pvc -interaction=nonstopmode
\documentclass[line,overlap,10pt]{res}

\usepackage{hyperref}
\usepackage{libertine}
\usepackage{xcolor}

\renewcommand{\namefont}{\LARGE\textit}

\newenvironment{myitemize}
{ \vspace{-1.5\topsep} \begin{itemize} \setlength\itemsep{0em}}
{ \end{itemize} \vspace{-0.5\topsep}}

\def\entry#1#2#3#4#5
{
  {#1}#2 \hfill #4\\ 
  \textit{#3}\\
  \begin{myitemize}
  \item #5
  \end{myitemize}
}

\def\authorlist#1 { {\footnotesize #1} }
\def\textsb#1 { {\libertineSB #1 }}
\def\happy {\hspace{-1em} {\color{magenta}{$\star$}}}

\def\changemargin#1#2{\list{}{\rightmargin#2\leftmargin#1}\item[]}
\let\endchangemargin=\endlist
\newenvironment{publist}
{ \begin{changemargin}{0em}{0em}  }
{ \end{changemargin} }

\begin{document}

\name{Jeffrey Chang}
\address{
    \href{mailto:jeffrey_chang@g.harvard.edu}{jeffrey\_chang@g.harvard.edu}
    \hspace{2em} 
    \href{https://scholar.google.com/citations?user=INSgKl8AAAAJ}{Google Scholar} 
    \hspace{2em} 
    \href{https://jeffjar.me}{Personal Website}
}

\begin{resume}

\section{Education}

Ph.D. candidate in Physics, Harvard University \hfill 2020--
\\
B.S. in Physics, Stanford University (GPA: 4.03) \hfill 2016--`20

% GPA: 4.03 (in major: 4.04)
 
%Lynbrook High School, San Jose, CA \hfill 2016 \\
%GPA: 4.40, \textit{Valedictorian}

\section{Career}

\entry{Graduate Researcher}{ in Nicholas Polizzi's lab}{Dana Farber Cancer Institute and Harvard Medical School}{2022--}{De novo protein design of ligand-binding proteins for single-molecule proteomics}

\entry{Graduate Researcher}{ in Wesley Wong's Lab}{Wyss Institute, Boston Children's Hospital, and Harvard Medical School}{2021--`22}{Single-molecule force spectroscopy and Bayesian inference for polyclonal antibodies}

\entry{Graduate Researcher}{ in Michael Desai's lab}{Harvard Dept.\ of Organismic and Evolutionary Biology}{2020--`22}{High-throughput measurements of antibody binding affinities with yeast display}

\entry{Biophysics / Statistical Modeling Consultant}{}{Manifold Biotechnologies, Inc.}{2020--}{Algorithmic development of a platform for multiplexed quantification of barcoded proteins}

% \entry{Textbook Author}{ with Prof.\ Steven Kivelson and Dr.\ Jack Jiang}{Princeton University Press}{2019--`24}{``Statistical Mechanics of Phases and Phase Transitions''}

\entry{Undergraduate Researcher}{ in Steven Boxer's lab}{Stanford Dept.\ of Chemistry}{2017--`19}{X-ray crystallography to study photochemical pathways in fluorescent proteins}

\entry{Software Engineering Intern}{}{Schr{\"o}dinger, Inc.}{2017}{Helped develop python GUI for protein structure visualization}

% \textit{Science Educator}, Springlight Education Institute \hfill 2015--2016\\
% \begin{myitemize}
%     \item Designed curriculum and taught high-school level classes on \\
%         physics, chemistry, and biology
% \end{myitemize}

% \textit{Researcher}, Stanford School of Medicine, Khatri Lab\hfill 2015\\
% \begin{myitemize}
%     \item Semi-supervised machine learning of mRNA microarray data to \\predict autoimmune drug response
% \end{myitemize}

% \textit{Researcher}, Stanford Dept.\ of Linguistics, with Prof.\ Penelope Eckert \hfill 2015\\
% \begin{myitemize}
%     \item Sociolinguistic fieldwork to measure the California Vowel Shift \\in Bay Area teenagers
% \end{myitemize}

\section{Teaching Assistant}

Harvard Life Sciences 50: Integrated Science \hfill Winter 22-23 \\
Harvard Applied Math 104: Complex and Fourier Analysis \hfill Autumn 21-22 \\
Stanford Physics 216: Back of the Envelope Physics \hfill Autumn 19-20 \\
Stanford Physics 63: Electricity, Magnetism, and Waves \hfill Winter 19-20
% \textit{Peer Tutor}, Stanford Center for Teaching and Learning \hfill 2019\\
% \begin{myitemize}
%     \item Tutored Stanford undergraduates in math and physics through\\
%         a free tutoring program
% \end{myitemize}

\section{Honors}
 
Harvard NSF-Simons Center Quantitative Biology Student Award\hfill 2022 \\
Harvard Dept. of Physics James Mills Peirce Fellowship\hfill 2020 \\
National Science Foundation Graduate Research Fellowship\hfill 2020 \\
Stanford Deans' Award for Academic Achievement\hfill 2020 \\
% Stanford Humanities and Sciences Undergraduate Prize in Music \hfill 2019\\
Stanford Undergraduate Research and Advising Small Grant\hfill 2019 \\
% Stanford Bio-X IIP Symposium Best Poster Award \hfill 2018 \\
Stanford Bio-X Undergraduate Fellow \hfill 2018
% US National Science Bowl 2nd place team captain \hfill 2016 \\
% California State Science Fair 2nd place \hfill 2016 \\
% US Physics Olympiad Semifinalist \hfill 2016 \\
% USA Computing Olympiad Platinum Division \hfill 2015 \\
% Jessica Saal Fellowship Award \hfill 2015
% Stanford Institutes of Medical Research Summer Research Program \hfill 2015

\section{Skills}

\textit{Next-generation DNA sequencing.} Library preparation, data analysis \\
\textit{Yeast display.} Library design, cloning, transformation, flow cytometry \\
\textit{Biochemistry.} Protein expression and purification, UV-vis spectroscopy, X-ray crystallography \\
\textit{Statistics.} Bayesian inference, machine learning \\
\textit{Programming.} Python, C++, R

% \section{Interests}

% \textit{Chamber Music.} Financial officer of the Stanford Collaborative Orchestra \href{https://scor.stanford.edu}{[link]} \\
% \textit{Music Composition.} Horn sonatas, wind quintets, jazz tunes, and more \href{https://jeffjar.me/music.html}{[link]} \\
% \textit{French Horn.} Four years principal horn experience, ringer for local orchestras \\
% \textit{Jazz piano.} Active gigging musician with the Casual Business jazz combo \\
% \textit{French.} Fluent speaker with six years of coursework


\newpage

\section{Publications}
\happy \ = proudest works
\\

\begin{publist}
  \textsb{Serial femtosecond crystallography reveals that photoactivation in a fluorescent protein proceeds via the hula twist mechanism}
  \\
  \authorlist{A.\ Fadini, C.D.M.\ Hutchison, D.\ Morozov, \underline{J.\ Chang}, K.\ Maghlaoui, S.\  Perrett, F.\ Luo, J.C.X.\ Kho, M.G.\ Romei, R.M.L.\ Morgan, C.M.\ Orr, V.\ Cordon-Preciado, T.\ Fujiwara, N.\ Nuemket, T.\ Tosha, R.\ Tanaka, S.\ Owada, K.\ Tono, S.\ Iwata, S.G.\ Boxer, G.\ Groenhof, E.\ Nango, J.\ van Thor}
  \\
  \textit{Journal of the American Chemical Society,}
  \textbf{145}, 29,
  15796-15808
  (2023).
  \href{https://pubs.acs.org/doi/full/10.1021/jacs.3c02313}{[link]}
  \\

  \happy \textsb{Resolving Molecular Heterogeneity with Single-Molecule Centrifugation}
    \\
    \authorlist{Y.\ Luo‡, \underline{J.\ Chang‡}, D.\ Yang‡, J.\ S.\ Bryan IV, M.\ MacIsaac, S.\ Pressé, W.\ P.\ Wong}
    \\
    \textit{Journal of the American Chemical Society,}
    \textbf{145}, 6, 
    3276-3282
    (2023).
    \href{http://dx.doi.org/10.1021/jacs.2c11450}{[link]}
    \\

    \textsb{The landscape of antibody binding affinity in SARS-CoV-2 Omicron BA.1 evolution}
    \\
    \authorlist{A.\ Moulana‡, T.\ Dupic‡, A.M.\ Phillips‡, \underline{J.\ Chang‡}, A.A.\ Roffler, A.J.\ Greaney, T.N.\ Starr, J.D.\ Bloom, M.M.\ Desai}
    \\
    \textit{eLife},
    \textbf{12},
    e83442
    (2023).
    \href{https://elifesciences.org/articles/83442}{[link]}
    \\

    \textsb{Torsional Diffusion for Molecular Conformer Generation}
    \\
    \authorlist{B.\ Jing‡, G.\ Corso‡, \underline{J.\ Chang}, R.\ Barzilay, T.\ Jaakkola}
    \\
    \textit{Advances in Neural Information Processing Systems},
    \textbf{35},
    24240-24258 (2022).
    \href{https://openreview.net/forum?id=w6fj2r62r_H}{[link]}
    \\

    \textsb{Compensatory epistasis maintains ACE2 affinity in SARS-CoV-2 Omicron BA.1}
    \\
    \authorlist{A.\ Moulana‡, T.\ Dupic‡, A.M.\ Phillips‡, \underline{J.\ Chang‡}, S.\ Nieves, A.A.\ Roffler, A.J.\ Greaney, T.N.\ Starr, J.D.\ Bloom, M.M.\ Desai}
    \\
    \textit{Nature Communications},
    \textbf{13},
    7011
    (2022).
    \href{https://doi.org/10.1038/s41467-022-34506-z}{[link]}
    \\

    \textsb{Binding affinity landscapes constrain the evolution of broadly neutralizing anti-influenza antibodies}
    \\
    \authorlist{A.M.\ Phillips, K.R.\ Lawrence, A.\ Moulana, T.\ Dupic, \underline{J.\ Chang}, M.S.\ Johnson, I.\ Cvijovic, T.\ Mora, A.M.\ Walczak, M.M.\ Desai}
    \\
    \textit{eLife},
    \textbf{10},
    e71393
    (2021).
    \href{https://doi.org/10.7554/eLife.71393}{[link]}
    \\

    \happy \textsb{Structural Evidence of Photoisomerization Pathways in Fluorescent Proteins}
    \\
    \authorlist{\underline{J.\ Chang}, M.G.\ Romei, S.G.\ Boxer}
    \\
    \textit{Journal of the American Chemical Society},
    \textbf{141}, 39,
    15504-15508
    (2019).
    \href{http://dx.doi.org/10.1021/jacs.9b08356}{[link]}
\end{publist}

\section{Books}

\bigskip
\bigskip
\begin{publist}
\happy \textsb{Statistical Mechanics of Phases and Phase Transitions} 
\\
{Steven A.\ Kivelson, Jack M.\ Jiang, \underline{Jeffrey Chang}} 
\\
(Princeton University Press, 2024)
\href{https://press.princeton.edu/books/hardcover/9780691249742/statistical-mechanics-of-phases-and-phase-transitions}{[website]}
\end{publist}

% \section{Patents}

\end{resume}

\vfill\hfill{\scriptsize Last updated on \today.}
\end{document}
